Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2020-05-06 Manuscript/manuscript.Rmd
Add discussion point
methods edits (data sources section)

Biological replicate [??? Didn't you use combined Arrowhead calls? Replicates seem irrelevant] Hi-C data were downloaded from GEO GSE63525 [@rao20143d] (Supplementary Table 1) for the GM12878 and K562 cell lines. The autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries were obtained from Hi-C data at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolution using the ARROWHEAD algorithm [@durand2016juicebox]. TAD boundaries called on chromosome 9 were omitted from all downstream analyses, for all resolutions and cell lines, due to the sparsity of the contact matrix at the 10 kb resolution for the K562 cell line. [??? Can you look up closer? If Arrowhead could call boundaries at 5kb, but not 10kb, it is strange] Cell type-specific genomic annotations (BroadHMM chromatin segmentations, histone modifications, and transcription factor binding sites) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (GRCh37/hg19 human genome assembly, Supplementary Table 2). [??? Change "cis-regulatory elements (CRE)" to "C]

@@

@@

**Supplementary Table 1.** A complete list of the Hi-C data libraries obtained from GEO GSE63525 [@rao20143d] used to obtain the locations of topologically associating domains for ARROWHEAD, as well as the locations for the cell line specific .txt files of loop boundaries obtained by PEAKACHU [@salameh2019supervised].

>>>>

Within this study we used both TAD boundary and loop boundary data derived from the publically available tools ARROWHEAD [@durand2016juicebox] and PEAKACHU [@salameh2019supervised] respectively. ARROWHEAD is part of the Juicer suite of tools for Hi-C data analysis and visualization. To obtain TAD boundaries we applied ARROWHEAD from downloaded primary Hi-C data for the GM12878 and K562 cell lines from Geo GSE63525 [@rao20143d] (libraries HIC001-HIC018 and HIC069-HIC074 for GM12878 and K562 respectively) produced with the MboI restriction enzyme (Supplementary Table 1). The contact matrices were constructed from all read pairs that uniquely align to the genome (MAPQ>0). The default tools for ARROWHEAD were used when extracting the autosomal genomic coordinates (GRCh37/hg19 human genome assembly) of TAD boundaries at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions (Additional File 1). For chromatin loop boundaries, we used loops identified by PEAKACHU at 10 kb for the GM12878 and K562 cell line [@salameh2019supervised]. Unique boundaries were considered as the midpoints within the coordinate of each chromatin loop. Chromosome 9 was excluded from all downstream analyses due to the sparsity of the contact matrix at the 5 kb and 10 kb resolutions for the K562 cell line. [??? Can you look up closer? If Arrowhead could call boundaries at 5kb, but not 10kb, it is strange; !!!https://groups.google.com/forum/#!searchin/3d-genomics/chr9$20from$20k562%7Csort:date]. Cell type-specific genomic annotations (BroadHMM chromatin segmentations, histone modifications, and transcription factor binding sites) were obtained from the UCSC Genome Browser Database [@Tyner:2017aa] (GRCh37/hg19 human genome assembly, Supplementary Table 2). [??? Change "cis-regulatory elements (CRE)" to "C; !!!fixed]

@@

<!-- Discuss advantages and disadvantages of Balanced Accuracy. The disadvantage is that we restrict TP to the originally detected TAD boundaries. While there are likely many more that couldn't be detected but are TP. We currently count them as FP -->

@@

**Additional File 1**. An example script for applying the ARROWHEAD tool to in situ Hi-C data (HIC001-HIC018) for resolutions 5kb, 10kb, 25kb, 50kb, 100kb to obtain chromosome-specific TAD boundaries on the GM12878 cell line.

**Supplementary Table 1.** A complete list of the Hi-C data libraries obtained from GEO GSE63525 [@rao20143d] used to obtain the locations of topologically associating domains for ARROWHEAD, as well as the locations for the cell line specific .txt files of loop boundaries obtained by PEAKACHU. [@salameh2019supervised].
